---
title: "index"
author: "Mia Minkin and Francesco de Luca"
format: html
editor: visual
chunk_output_type: console
self-contained: true
editor_options: 
  chunk_output_type: console
---

**Data Source**

"https://electionstudies.org/data-center/2020-time-series-study/"

**Loading packages**

```{r, echo=FALSE}
library(tidyverse)
library(gridExtra)
```

**Loading data**

```{r}
ANES_2020<-read_csv("data/2020_ANES.csv")

#Feeling thermometer of Democrats 
democrats_ANES_2020<-filter(ANES_2020,V201018==1) 
democrats_ANES_2020<-filter(democrats_ANES_2020,V201156>0&V201156<998)

#Feeling thermometer of Republicans 
republicans_ANES_2020<-filter(ANES_2020,V201018==2)
republicans_ANES_2020<-filter(republicans_ANES_2020,V201157>0&V201157<998)
```

## **Visualization 1: Feeling Thermometer**

**Visualization 1.1: Democrat feelings towards Democrats**

```{r}
feeling_thermometer_democrats<- 
  ggplot(data=democrats_ANES_2020, aes(x=V201018,y=V201156))+ 
  geom_point(color="blue")+ 
  scale_x_continuous(breaks=seq(1,1,by=1), 
                     labels=c("1"="Democrat"))+ 
  scale_y_continuous(breaks=seq(0,100,by=10))+ 
  xlab("Party Affiliation")+ 
  ylab("Feeling Thermometer")+ 
  ggtitle("Democrat Feeling Thermometer", "How Democrats Feel About Their Party")+
  theme_classic()
feeling_thermometer_democrats
```

**Visualization 1.2: Republican feelings towards Republicans**

```{r}
feeling_thermometer_republicans<- 
  ggplot(data=republicans_ANES_2020, aes(x=V201018,y=V201157))+ 
  geom_point(color="red")+ 
  scale_x_continuous(breaks=seq(2,2,by=1), 
                     labels=c("2"="Republican"))+ 
  scale_y_continuous(breaks=seq(0,100,by=10))+ 
  xlab("Party Affiliation")+ 
  ylab("Feeling Thermometer")+ 
  ggtitle("Republican Feeling Thermometer", "How Republicans Feel About Their Party")+
  theme_classic()
feeling_thermometer_republicans
```

**Complete Visualization 1**

```{r}
grid.arrange(feeling_thermometer_democrats,feeling_thermometer_republicans,ncol=2,nrow=1)
```

**Summary of visualization 1**

The visualization created shows how respondents who identify as Democrats feel towards other Democrats as well as how respondents who identify as Republicans feel towards Republicans. As seen in the visualization, it is clear that Democrats think more highly of Democrats than Republicans do of Republicans. This can be seen through the clustering towards the more positive feelings, around the mid 70s and higher on the feeling thermometer as opposed to the Republican graph which indicates less clustering in general.

## **Visualization 2: Who Donates to Individual Candidates More?**

**Visualization 2.1: Democrats Who Donated Money**

**Cleaning the data**

```{r}
#Democrats who donated money
democrat_donations<-filter(ANES_2020,V201018==1)
democrat_donations<-filter(democrat_donations,V202017>0)
count(democrat_donations,democrat_donations$V202017==1)
dem_donations<-as.data.frame(table(democrat_donations$V202017))
colnames(dem_donations)[1]<-"Donated"
colnames(dem_donations)[2]<-"Count"
```

**Graph**

```{r}
dem_donations_graph<-
ggplot(data=dem_donations,
       aes(x=Donated,y=Count))+
  geom_bar(stat="identity", fill="blue")+
  scale_x_discrete(labels=c("1"="Donated","2"="Didn't Donate"))+
  geom_text(aes(label=Count), hjust=0, size=4)+
  xlab("Did Respondent Donate?")+
  ylab("Number of People")+
  ggtitle("Donations by Democrats",
          "Number of Democrats Who Donated to a Candidate vs. Did Not Donate")+
  theme_classic()+
  coord_flip()
dem_donations_graph
```

**Visualization 2.2: Republicans Who Donated Money**

**Cleaning the data**

```{r}
republican_donations<-filter(ANES_2020,V201018==2)
republican_donations<-filter(republican_donations,V202017>0)
count(republican_donations,republican_donations$V202017==1)
republican_donations<-as.data.frame(table(republican_donations$V202017))
colnames(republican_donations)[1]<-"Donated"
colnames(republican_donations)[2]<-"Count"
```

**Graph**

```{r}
republican_donations_graph<-
ggplot(data=republican_donations,
       aes(x=Donated,y=Count))+
  geom_bar(stat="identity", fill="red")+
  scale_x_discrete(labels=c("1"="Donated","2"="Didn't Donate"))+
  geom_text(aes(label=Count), hjust=0, size=4)+
  xlab("Did Respondent Donate?")+
  ylab("Number of People")+
  ggtitle("Donations by Republicans",
          "Number of Republicans Who Donated to a Candidate vs. Did Not Donate")+
  theme_classic()+
  coord_flip()
republican_donations_graph
```

**Complete Visualization 2**

```{r}
grid.arrange(dem_donations_graph,republican_donations_graph,ncol=1, nrow=2)
```

**Summary of visualization 2**

The second visualization shows the number of respondents who did and did not donate to an individual candidate in the 2020 election broken down by party. Looking at the two graphs next to one another, you can see that Democrats donated at a higher frequency than Republicans did. This does not speak to the amount donated by the respondents, but indicates that there were more individual donors among Democrat respondents than Republican respondents.

## **Visualization 3: Voting Preferences of Muslims**

**Loading Data**

```{R}
#Muslim voting preferences
muslim_preferences<-filter(ANES_2020,V201457x==720)
muslim_preferences<-filter(muslim_preferences,V202073>0&V202073<3)
count(muslim_preferences,muslim_preferences$V202073==1)
count(muslim_preferences,muslim_preferences$V202073==2)
muslim_preferences<-as.data.frame(table(muslim_preferences$V202017))
muslim_preferences
colnames(muslim_preferences)[1]<-"Candidate"
colnames(muslim_preferences)[2]<-"Frequency"
rownames(muslim_preferences)[1]<-"Biden"
rownames(muslim_preferences)[2]<-"Trump"
muslim_preferences
```

**Graph**

```{R}
muslim_preferences_graph<-
ggplot(data=muslim_preferences,
       aes(x=Candidate,y=Frequency))+
  geom_bar(stat="identity", fill="purple")+
  scale_x_discrete(labels=c("1"="Biden","2"="Trump"))+
  geom_text(aes(label=Frequency), hjust=0, size=4)+
  xlab("Who did the respondent vote for?")+
  ylab("Frequency")+
  ggtitle("Voting Preferences of Muslims",
          "Number of Muslims Who Voted For Trump vs. Biden")+
  theme_classic()+
  coord_flip()
muslim_preferences_graph
```

**Summary of visualization 3**

The distribution indicates that the overwhelming majority of the sampled population who identifies as Muslim voted for Trump at the last presidential elections. Such a result clashes with the expected frequency of self-identified Muslim respondents, who should have favored the Democratic candidate.

##  **Visualization 4: Voting Preferences of Catholics** **Loading Data**

```{R}
#Catholic voting preferences
catholic_preferences<-filter(ANES_2020,V201457x==400)
catholic_preferences<-filter(catholic_preferences,V202073>0&V202073<3)
count(catholic_preferences,catholic_preferences$V202073==1)
count(catholic_preferences,catholic_preferences$V202073==2)
catholic_preferences<-as.data.frame(table(catholic_preferences$V202017))
colnames(catholic_preferences)[1]<-"Candidate"
colnames(catholic_preferences)[2]<-"Frequency"
rownames(catholic_preferences)[1]<-"Biden"
rownames(catholic_preferences)[2]<-"Trump"
catholic_preferences
```

**Graph**

```{R}
#Graph
catholic_preferences_graph<-
ggplot(data=catholic_preferences,
       aes(x=Candidate,y=Frequency))+
  geom_bar(stat="identity", fill="gold")+
  scale_x_discrete(labels=c("1"="Biden","2"="Trump"))+
  geom_text(aes(label=Frequency), hjust=0, size=4)+
  xlab("Who did the respondent vote for?")+
  ylab("Frequency")+
  ggtitle("Voting Preferences of Catholics",
          "Number of Catholics Who Voted For Trump vs. Biden")+
  theme_classic()+
  coord_flip()
catholic_preferences_graph
```

**Summary of Visualization 4**

The distribution indicates that the overwhelming majority of the sampled population who identifies as Catholic voted for Trump at the last presidential elections. Such a result is, unexpectedly, in line with the result for the self-identified sampled Muslims, who also voted for Trump.
